QPLIB: A Library of Quadratic Programming Instances

### 2018-02-08 QPLIB-2.2.tex
add doubt on choice of references

This description is deliberately coarse; each of these classes can be subdivided into several others on the grounds of more detailed information about structures present in their constraints/objective function. These can have a significant algorithmic impact, and therefore can be of interest to researchers. Common structures are, e.g., network flows \cite{FrFG16,FrGaSc14,FrGaSt16a,FGGP11,tadayon-smith:2013} or knapsack-type linear constraints \cite{FrFG16,FrGo13b,FGGP11}, and semi-continuous variables \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe06a,FrGe07a,FrGe09a,FGGP11}, or the fact that a nonconvex quadratic objective function/constraint can be reformulated as a second-order cone (hence, convex) one \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe09a,FGGP11}. It would be very hard to collect a comprehensive list of all types of structures that might be of interest to any individual researcher, since these are as varied as the different possible approaches for specialized sub-classes of QP. For this reason we do not attempt such a more refined classification, and limit ourselves to the coarser one described in this section.

>>>>

This description is deliberately coarse; each of these classes can be subdivided into several others on the grounds of more detailed information about structures present in their constraints/objective function. These can have a significant algorithmic impact, and therefore can be of interest to researchers. Common structures are, e.g., network flows \cite{FrFG16,FrGaSc14,FrGaSt16a,FGGP11,tadayon-smith:2013} or knapsack-type linear constraints \cite{FrFG16,FrGo13b,FGGP11}, and semi-continuous variables \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe06a,FrGe07a,FrGe09a,FGGP11}\todo{SV: do we really need 7 Frangioni et.al citations for semi-continuous variables?}, or the fact that a nonconvex quadratic objective function/constraint can be reformulated as a second-order cone (hence, convex) one \cite{FrFG16,FrGaSc14,FrGaSt16a,FrGe09a,FGGP11}\todo{SV: 5 Frangioni et.al citations for SOC?}. It would be very hard to collect a comprehensive list of all types of structures that might be of interest to any individual researcher, since these are as varied as the different possible approaches for specialized sub-classes of QP. For this reason we do not attempt such a more refined classification, and limit ourselves to the coarser one described in this section.
